Lyman-$\alpha$ photons through rotating outflows

### 2018-03-31 paper/paper.tex
edit

\begin{abstract}
Outflows and rotation are two ubiquitous kinematic features in the gas
kinematics of galaxies.
Here we perform Monte Carlo radiative transfer simulations of outflowing
gas with additional solid body rotation to understand how these kinematic
features impact the morphology of the Lyman-$\alpha$ emission line.
We explore a range of Hydrogen optical depth of
$10^5\leq\tauh\leq10^7$, rotational velocity $0\leq \vrot/\kms \leq 100$ and
outflow velocity $0\leq \vout/\kms\leq 50$.  
We find three important consequences of rotation.
First, it introduces a dependency with viewing angle; second it
produces a line broadening and third it increases the flux at the
line's center.
We also develp a semi-analytic model that modifies the spectra of
pure outflow simulations and manages to reproduce the line widths
and flux change at the line's center within a $7\%$ and $50\%$
precision, respectively.
\end{abstract}

>>>>

\begin{abstract}
Outflows and rotation are two ubiquitous kinematic features in the gas
kinematics of galaxies.
Here we perform Monte Carlo radiative transfer simulations of outflowing
gas with additional solid body rotation to understand how these kinematic
features impact the morphology of the Lyman-$\alpha$ emission line.
We explore a range of Hydrogen optical depth of
$10^5\leq\tauh\leq10^7$, rotational velocity $0\leq \vrot/\kms \leq 100$ and
outflow velocity $0\leq \vout/\kms\leq 50$.  
We find three important consequences of rotation.
First, it introduces a dependency with viewing angle; second it
produces a line broadening and third it increases the flux at the
line's center.
We also test a semi-analytic model that modifies the spectra of
pure outflow simulations and manages to reproduce the line widths
and flux change at the line's center within a $7\%$ and $50\%$
precision, respectively.
We argue that rotation is a required kinematic feature to take into
account for a correct interpretation of \lya spectra in systems where
rotation is evidences through kinematic maps but also in other
systems, such as Green Pea galaxies, where a strong \lya emission at
the line's center could be due to rotational kinematics. 
\end{abstract}
